Adaptive evolution with aneuploidy and mutation

### 2021-12-27 ms/ms.tex
moved fig from supp to text
revised results

However, a model without aneuploidy, i.e. where the aneuploidy gain rate is fixed at zero $\delta=0$, cannot explain the data~(\autoref{fig:2n*-fixation} and \autoref{fig:likelihood}). The estimated parameter values without aneuploidy are:
mutation rate, $\mu=1.251\substack{+0.146 \\ -0.177}\times10^{-8}$,
2n+1 fitness - $1.01\substack{+0.001 \\ -0.002}$,
2n+1* fitness - $1.011\substack{+0.001 \\ -0.001}$,
%TODO why do you have fitness of aneuploidy when there is no aneuploidy?
2n* fitness - $1.011\substack{+0.001 \\ -0.001}$. 
We can see that mutation rate for this model is much lower than for the model with aneuploidy. Higher mutation rate would cause quicker fixation of \eumt\ than expected by the experiment ( \autoref{fig:2n*-fixation} blue bar). Thereby, adding aneuploidy to the model, helps to attain good fit with higher mutation rate.
% TODO WAIC?

@@

% Fig single-locus model with and without aneuploidy
\begin{figure}[b!]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
      \caption{
        \textbf{A. With aneuploidy}
      }
      \centering
      \includegraphics[height=1.8in]{../figures/likelihood-plot.pdf}      
      \label{fig:likelihood-with-aneuploidy}
  \end{subfigure}%
  \\
  \begin{subfigure}[t]{0.5\textwidth}
  	  \caption{
        \textbf{B. Without aneuploidy}
      }
      \centering
      \includegraphics[height=1.8in]{../figures/likelihood-noaneuploidy-plot.pdf}      
      \label{fig:likelihood-without-aneuploidy}
  \end{subfigure}
  \caption{
  % TODO change x label - "Time to fixation of 2n*"
  % plot both lines on one panel with two colors (blue and red for with and without? choose nice color, not the default 'r' and 'b'!), make the without in dashed.
    \textbf{Single-locus model fit with and without aneuploidy.} Cumulative distribution of the time to fixation of \eumt\ in 10,000 simulations using the MAP estimate with and without aneuploidy (i.e., $\delta=0$ is fixed).
    \textbf{(B)} Simulations parameters are from the maximum a posterior estimation of the single-locus model \emph{without} aneuploidy fit. 
     The MAP likelihood (\autoref{eq:heatstress-likelihood}) is 0.86 and 0.75 with and without aneuploidy. % TODO likelihood ratio test? bayes factor? no sense in just giving the likelihoods.
  }
  \label{fig:likelihood}
\end{figure}

>>>>

However, a model without aneuploidy where the aneuploidy rate is fixed at zero, $\delta=0$, cannot explain the experimental observations~(Figures~\ref{fig:2n*-fixation} and \ref{fig:likelihood}). The estimated parameter values without aneuploidy are:
mutation rate, $\mu=1.251\substack{+0.146 \\ -0.177}\times10^{-8}$,
%2n+1 fitness - $1.01\substack{+0.001 \\ -0.002}$,
%2n+1* fitness - $1.011\substack{+0.001 \\ -0.001}$,
%TODO why do you have fitness of aneuploidy when there is no aneuploidy?
fitness of mutant, $w_{2n^*}=1.011\substack{+0.001 \\ -0.001}$. 
We can see that the mutation rate estimate in this model is much lower than in the model with aneuploidy. Higher mutation rate would cause quicker fixation of \eumt\ than in the experimental obvservations (\autoref{fig:2n*-fixation}). Thus, even disregarding the appearance of trisomic cells in the experiment, the evidence supports the inclusion of aneuploidy in the model.
% TODO WAIC?

% Fig single-locus model with and without aneuploidy
\begin{figure}[b!]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
      \caption{
        \textbf{A. With aneuploidy}
      }
      \centering
      \includegraphics[height=1.8in]{../figures/likelihood-plot.pdf}      
      \label{fig:likelihood-with-aneuploidy}
  \end{subfigure}
  \begin{subfigure}[t]{0.45\textwidth}
  	  \caption{
        \textbf{B. Without aneuploidy}
      }
      \centering
      \includegraphics[height=1.8in]{../figures/likelihood-noaneuploidy-plot.pdf}      
      \label{fig:likelihood-without-aneuploidy}
  \end{subfigure}
  \caption{
  % TODO change x label - "Time to fixation of 2n*"
  % plot both lines on one panel with two colors (blue and red for with and without? choose nice color, not the default 'r' and 'b'!), make the without in dashed.
    \textbf{Single-locus model fit with and without aneuploidy.} Cumulative distribution of the time to fixation of \eumt\ in 10,000 simulations using the MAP estimate with and without aneuploidy (i.e., $\delta=0$ is fixed).
    \textbf{(B)} Simulations parameters are from the maximum a posterior estimation of the single-locus model \emph{without} aneuploidy fit. 
     The MAP likelihood (\autoref{eq:heatstress-likelihood}) is 0.86 and 0.75 with and without aneuploidy. % TODO likelihood ratio test? bayes factor? no sense in just giving the likelihoods.
  }
  \label{fig:likelihood}
\end{figure}

@@
